### 2019-08-09 Thesis/pages/experiments.tex
Changes; - Added further discussion to the report

\section{Experiment 2}
% Demographic
% Results

@@

\subsection*{Limitations}
Due to multiple attacks occurring for one participant the rate of success cannot be

\subsection{Comparison to alternative literature}
\todo{Compare to the other similar papers, is this higher or lower than other papers?}

% # Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols

% Set of 4 words compared from a dictionary of 1024 words (10-bits per word)

% 	- Near matches differ by a single word (No measure of similarity) randomly decided word

% 	- FP (Security faliure)
% 	- FN (Non-security faliure)

% 	Total: 3.3% (FP) - 16.7% (FN)

% 	Only 30 participants

% # Unicorns

% 	- 16 words long

% 	"Our participants were recruited from MTurk, which is not
% 	representative of the general U.S. population; MTurk workers
% 	have been found to be younger and better educated [15]."

% 	14% missed the simulated attacks

@@

Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation. Due to varying availability of resources each computation has a varying hashing speed. This, however, has been normalized by the introduction of the "GPU Day" metric. This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.

>>>>

\section{Experiment 2}
\label{sec:exp2}
% Demographic
% Results

@@

\subsection*{Limitations}
During this study the main task was to perform the authentication ceremony a large number of times. In the real-world the ceremony is a secondary task due to it not strictly being required. This alongside the potential for users to downplay the possibility of attack leads to the conclusion that these results have limited applicability in a real-world setting. The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their participant and not just aim to complete the task as quickly as possible. This, therefore, means in a real-world setting the success rates could be even higher.

\todo{Include email example of user assuming error over attack}.

\subsection{Comparison to alternative literature}
This section will aim to compare the results of the experiment to similar literature.

Work by Kainda \textit{et al.}\cite{kainda2009usability} (previous discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment. They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated. Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.

However, with those aspect in mind Words received an overall success rating of 3.3\%, considerably lower than that of this study. The results presented in this experiment in the worst case presented almost 3 times as many successful attacks.

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success for the PGP Word list was 8.78\%. As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''. Therefore, the results presented in this section are substantially higher than this paper, where again the success rate is almost 3 times higher.

The final relevant paper to compare is that of Tan \textit{et al.}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}. The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference between the attack successes.

In conclusion, all similar literature had much lower attack success rates that the results presented in this experiment. With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success. Furthermore, the consideration for similarity of words that the other papers have not considered could have also resulted in the higher attack success rates.

@@

Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation. Due to varying availability of resources each computation has a varying hashing speed. This, however, has been normalized by the introduction of the "GPU Day" metric. This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU. As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.

When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users. This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user assuming the success rate is consistent across all keys.

### 2019-08-09 Thesis/pages/implementation.tex
Changes; - Added further discussion to the report

\todo{Talk here about the interesting and challenges that were overcome}

@@

Mass checking of fingerprints is the tools main abilities as it allows for millions of keys to be checked with a very small amount of overhead. This is achieved through the use of a bloom filter. A bloom filter is a probabilistic data structure that allows efficient checking for present of an element in a set. It is effectively a very large array of booleans that state wether an element is present. A position in the array is decided by a hashing algorithm. This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$). This then means checking the presence of an element in the set will just mean hashing the target and checking the elements returned. This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set. This is the only data structure that provides this characteristic.

@@

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used as the application. It provided functionality to easily present questions and record their responses. However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality other solution was required. This was solved by Google's  App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form. This allowed the re-sampling of matches each time a user submitted a response.

@@

\section{MainExperiment}
In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.

\todo{What interesting aspects do I want to talk about here?}

>>>>

This chapter will discuss implementation details of the project. Instead of explaining all the technical achievements in detail, the most interesting ones will be discussed alongside the respective challenges encountered.

@@

Mass checking of fingerprints is the tools main abilities as it allows for millions of keys to be checked with a very small amount of overhead. This is achieved through the use of a bloom filter. A bloom filter is a probabilistic data structure that allows efficient checking for presence of an element in a set. It is effectively a very large array of booleans that state wether an element is present where the position in the array is decided by a pre-defined hashing algorithm. This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$). This then means checking the presence of an element in the set will just means hashing the target and checking the indices returned. This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set. This is the only data structure that provides this useful characteristic.

@@

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided functionality to easily present questions and record their responses. However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality a solution was required. This was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form. This allowed the re-sampling of matches each time a user submitted a response.

@@

\section{MainExperiment}
In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required. The front-end is developed in Javascript with a Python-Flask backend that acts as the webpages functionality. A number of end points are exposed like \verb|get_audio| or \verb|get_words| that are requested and displayed on the front-end.

One of the main problems encountered was the handling of each user's session. Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly know as a ``Lost update''. This was due to the user session being stored in the \verb|session| cookie. When sending off a request the session cookie is included in the header, the code will then utilise the data within the cookie to make decision and alter state, the updated state is then returned as a cookie in the response. If, however, another request is executed before the first has completed, the second request is using the context of the first request and, thus, any alterations made by the first will be completely lost.

\begin{figure}[!h]
  \centering
  \begin{sequencediagram}
    \newthread{A}{Client}{}
    \newinst[2]{B}{get\_audio()}{}
    \newinst[2]{C}{get\_words()}{}

    \begin{call}{A}{}{B}{}
    \begin{call}[1]{A}{}{C}{}
    \end{call}
    \end{call}

    \node[anchor=east] (c0) at (0.75, -1.325) {$c$};
    \node[below of=c0, yshift=.4cm] (c1) {$c$};
    \node[below of=c1, yshift=.4cm] (c2) {\textbf{\st{$c_{1}$}}};
    \node[below of=c2, yshift=.4cm] (c3) {$c_2$};
  \end{sequencediagram}
  \caption{Sequence diagram for the `Lost Update' problem}
  \label{fig:cookie}
\end{figure}

Figure \ref{fig:cookie} shows this problem visually. As it can be seen the response cookie $c_2$ is based of the old data of $c$ and, therefore, when returned will remove the progress of $c_1$.

To keep the complexity of the backend low it was opted to solve this problem by restricting the user via the UI, when a button was clicked all other operations were disabled until a response was received. This stopped the possibility of sending off another request while another is still processing.

I order to collate data for results later in the process state had to be saved. One potential solution would be to format the data and save it as a .csv file. However, this is a static way of data persistence and would require alteration every time the data schema was modified. The chosen solution utilized a python object serialization library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}. This library saves the an instance of a class as a file. This file then can be used to load the instance of the class back into the program. This allows changes to the object to filter down through the program and keeps the design of the application fluid. For example, after initial feedback gathered about the application it was decided that a inclusion of `Round times' would be a useful addition. Edits were made to the \verb|experiment| class and the changes propagated through the application, no changes were needed on the save functionality. To distinguish between old and new save formats a version number was used.

### 2019-08-09 Thesis/pages/introduction.tex
Changes; - Added more content to Thesis background
Changes; - Added scripts for processing Similar Words results - Added more content to the Thesis
Changes; - Added further discussion to the report

The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
verification is an ever more important task. One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack. A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data. A countermeasure for this is the verification of each parties' fingerprint. \textbf{[...]}

>>>>

The increasing use of public key cryptography by instant messaging and secure email means key fingerprint  verification is an ever more important task.

One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack. A MiTM attack involves an attacker impersonating one or both sides of a connection. MiTM attacks can fully circumvent the encryption as it allows an attacker to read all of the encrypted data.

A countermeasure for this is the verification of each parties' key fingerprint. A fingerprint is a small string of characters that is unique to each key pair. Therefore, it can be used as as a way of identification.

Fingerprints can come in a number of different encodings such as hexadecimal, words and even procedurally generated avatars. Previous research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}, alongside this the involvement of human based verification makes the designing the scheme to be user friendly is a task of upmost importance.

Humans have long been known as the most vulnerable part of any system. To combat this issue, solutions have been proposed to remove the manual verification with examples such as PGP's web-of-trust\cite{callas1998openpgp} and Namecoin\cite{kalodner2015empirical}. However, these suffer from user adoption due to perceived complexity. This leaves manual verification in the current position of being a difficult problem, where the proposed solutions need to sacrifice one of usability or security. Therefore, research into improving or creating new fingerprint encodings that work well with users remains massively relevant.

The report will asses the security and feasibility of attacking a fingerprint encoding known as ``Trustwords'' as it claims at this point have been unsubstantiated.

The report will be structured as follows:

\textbf{Chapter 2} provides any required background knowledge alongside a review on all relevant literature.

\textbf{Chapter 3} formally defines the aim of this report alongside the research questions the project aims to answer.

\textbf{Chapter 4} documents the prosed designs required to answer the research questions proposed in Chapter 3.

\textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.

\textbf{Chapter 6} presents and analyses all experimentation results of the project.

\textbf{Chapter 7} evaluates the success of the project alongside a discussion into relevant further work. The research aims proposed earlier in Chapter 3 will be used as evaluative metrics.

\textbf{Chapter 8} concludes the project with a culmination of the papers findings alongside the any conclusions that can be drawn from the research.
